---
title: "NHANES EAA and fatty acid intake: Analyses"
author: "Anne Bozack"
output: 
    html_document:
        code_folding: 
        toc: true
        toc_float: true
---


## Libraries
```{r, eval = F}
library(tidyverse)
library(survey) 
library(forcats)
library(jtools)
library(dplyr)
library(mice)
library(mitools)
library(svydiags)
library(kableExtra)
```

## Survey design
```{r, eval = F}
load("nhanes_fattyAcids_clean_data.RData")

# specify survey design
nhanesDesign <- svydesign(id = ~SDMVPSU,  # Primary Sampling Units (PSU)
                 strata  = ~SDMVSTRA, # Stratification used in the survey
                 weights = ~WTDN4YR,   # Survey weights (using those from DNAm dataset, may need to update)
                 nest    = TRUE,      # Whether PSUs are nested within strata
                 data    = df)       # specify dataset
dim(nhanesDesign)
# 2532  288

# subset survey design
nhanesDesign_use <- subset(nhanesDesign, use_fat)
dim(nhanesDesign_use)
# 2220  288

nhanesDesign_use_covar <- subset(nhanesDesign, use_fat_covar)
dim(nhanesDesign_use_covar)
# 1771  288
```

### Primary model - linear associations adjusted for age, age^2, gender, race/ethnicity, BMI, education, occupation, PIR, alcohol, smoking, and physical activity
```{r, eval = F}
# dataframe to store results
fat_res_alcSmkAct = data.frame(nutrient = rep(c('Total fat', 'Saturated fat', 'Monounsaturated fat', 'Polyunsaturated fat', 'P:S ratio', 'Omega-3', 'Omega-6'), each = 11),
  clock = rep(c('Horvath1', 'Horvath2', 'Hannum', 'Lin', 'Zhang', 'VidalBralo', 'PhenoAge', 'GrimAge2', 
        'DNAmTL', 'YangCell', 'DunedinPoAm'), times = 7),
  coef = NA, p = NA, CI_L = NA, CI_H = NA, n = NA)

# NHANES variable names
vars_fat = c('DRXTTFAT_log2', 'DRXTSFAT_log2', 'DRXTMFAT_log2', 'DRXTPFAT_log2', 'psatfatRatio', 'omega3_log2', 'omega6_log2')
vars_ead = c('HorvathAge', 'SkinBloodAge', 'HannumAge', 'LinAge', 'ZhangAge', 'VidalBraloAge', 'PhenoAge', 'GrimAge2Mort', 'HorvathTelo', 'YangCell_scale', 'DunedinPoAm_scale')

# functions to fill in table
popTable1 = function(tab, i, j, k){
    # i = EAD variable
    # j = fat variable
    # k = table row
    mod = svyglm(formula(paste0(vars_ead[i], " ~ ", vars_fat[j], " +
        RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
        BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
        factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
        design = nhanesDesign_use, 
        family = gaussian())
    tab[k,3] = summary(mod)$coef[2,1]
    tab[k,4] = summary(mod)$coef[2,4]
    tab[k,5] = confint(mod)[2,1]
    tab[k,6] = confint(mod)[2,2]
    tab[k,7] = nrow(mod$model)
    return(tab)
}

popTable2 = function(tab, vars_fat, vars_ead){
    k = 1
    for (j in 1:length(vars_fat)){
        for (i in 1:length(vars_ead)){
            tab = popTable1(tab, i, j, k)
            k = k + 1
        }
    }
    return(tab)
}

fat_res_alcSmkAct = popTable2(fat_res_alcSmkAct, vars_fat, vars_ead)

fat_res_alcSmkAct$B_CI = paste0(round(fat_res_alcSmkAct$coef, 2), ' ', fat_res_alcSmkAct$CI)

write.csv(fat_res_alcSmkAct, 'fat_res_alcSmkAct.csv')
```

```{r, warning=FALSE, message=FALSE, echo = F}
kable(fat_res_alcSmkAct) %>% kable_classic()
```



#### Omega-3 and omega-6 jointly adjusted model
```{r, eval = F}
# dataframe to store results
fat_res_alcSmkAct_omegas = data.frame(nutrient = rep(c('Omega-3', 'Omega-6'), each = 11),
  clock = rep(c('Horvath1', 'Horvath2', 'Hannum', 'Lin', 'Zhang', 'VidalBralo', 'PhenoAge', 'GrimAge2', 
        'DNAmTL', 'YangCell', 'DunedinPoAm'), times = 2),
  coef = NA, p = NA, CI_L = NA, CI_H = NA, n = NA, se = NA)

# NHANES variable names
vars_ead = c('HorvathAge', 'SkinBloodAge', 'HannumAge', 'LinAge', 'ZhangAge', 'VidalBraloAge', 'PhenoAge', 'GrimAge2Mort', 'HorvathTelo', 'YangCell_scale', 'DunedinPoAm_scale')

# functions to fill in table
popTable_omegas = function(tab, vars_ead){
    for (i in 1:length(vars_ead)){
        mod = svyglm(formula(paste0(vars_ead[i], " ~ omega3_log2 + omega6_log2 +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian())
        tab[i,3] = summary(mod)$coef[2,1]
        tab[i,4] = summary(mod)$coef[2,4]
        tab[i,5] = confint(mod)[2,1]
        tab[i,6] = confint(mod)[2,2]
        tab[i,7] = nrow(mod$model)
        tab[i,8] = summary(mod)$coef[2,2]
        tab[i+11,3] = summary(mod)$coef[3,1]
        tab[i+11,4] = summary(mod)$coef[3,4]
        tab[i+11,5] = confint(mod)[3,1]
        tab[i+11,6] = confint(mod)[3,2]
        tab[i+11,7] = nrow(mod$model)   
        tab[i+11,8] = summary(mod)$coef[3,2]
    }
    return(tab)
}

fat_res_alcSmkAct_omegas = popTable_omegas(fat_res_alcSmkAct_omegas, vars_ead)

fat_res_alcSmkAct_omegas$B_CI = paste0(round(fat_res_alcSmkAct_omegas$coef, 2), ' ', fat_res_alcSmkAct_omegas$CI)

write.csv(fat_res_alcSmkAct_omegas, 'fat_res_alcSmkAct_omegas.csv')

# calculate VIF
X = model.matrix(formula(" ~ omega3_log2 + omega6_log2 +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR"), data = df[df$use_fat_covar,])

# Horvath1
i = 1
mod = svyglm(formula(paste0(vars_ead[i], " ~ omega3_log2 + omega6_log2 +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian())
svyvif(mod, X = data.frame(X[,-1]), w = data.frame(df[df$use_fat_covar,])$WTDN4YR)
# $`Intercept adjusted`
#                                         svy.vif.m  reg.vif.m      zeta     varrho.m zeta.x.varrho.m      Rsq.m
# omega3_log2                              2.967946   3.212232 1309589.2 7.055276e-07       0.9239513 0.68868994
# omega6_log2                              3.597126   3.694117 1576102.2 6.178180e-07       0.9737444 0.72929935

# Horvath2
i = 2
mod = svyglm(formula(paste0(vars_ead[i], " ~ omega3_log2 + omega6_log2 +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian())
svyvif(mod, X = data.frame(X[,-1]), w = data.frame(df[df$use_fat_covar,])$WTDN4YR)
#                                         svy.vif.m  reg.vif.m      zeta     varrho.m zeta.x.varrho.m      Rsq.m
# omega3_log2                              2.530812   3.212232  725017.5 1.086687e-06       0.7878674 0.68868994
# omega6_log2                              3.167558   3.694117  996926.8 8.601034e-07       0.8574601 0.72929935

# Hannum
i = 3
mod = svyglm(formula(paste0(vars_ead[i], " ~ omega3_log2 + omega6_log2 +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian())
svyvif(mod, X = data.frame(X[,-1]), w = data.frame(df[df$use_fat_covar,])$WTDN4YR)
#                                         svy.vif.m  reg.vif.m      zeta     varrho.m zeta.x.varrho.m      Rsq.m
# omega3_log2                              2.623826   3.212232 1136967.8 7.184226e-07       0.8168234 0.68868994
# omega6_log2                              3.163919   3.694117 1575851.7 5.434998e-07       0.8564750 0.72929935

# Lin
i = 4
mod = svyglm(formula(paste0(vars_ead[i], " ~ omega3_log2 + omega6_log2 +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian())
svyvif(mod, X = data.frame(X[,-1]), w = data.frame(df[df$use_fat_covar,])$WTDN4YR)
#                                         svy.vif.m  reg.vif.m      zeta     varrho.m zeta.x.varrho.m      Rsq.m
# omega3_log2                              2.976786   3.212232 2997642.8 3.091440e-07       0.9267034 0.68868994
# omega6_log2                              3.291811   3.694117 3094102.4 2.879981e-07       0.8910955 0.72929935

# Zhang
i = 5
mod = svyglm(formula(paste0(vars_ead[i], " ~ omega3_log2 + omega6_log2 +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian())
svyvif(mod, X = data.frame(X[,-1]), w = data.frame(df[df$use_fat_covar,])$WTDN4YR)
#                                          svy.vif.m  reg.vif.m      zeta     varrho.m zeta.x.varrho.m      Rsq.m
# omega3_log2                              2.2000084   3.212232  86930.61 7.878522e-06       0.6848847 0.68868994
# omega6_log2                              2.8517601   3.694117 135412.20 5.700914e-06       0.7719733 0.72929935

# Vidal-Bralo
i = 6
mod = svyglm(formula(paste0(vars_ead[i], " ~ omega3_log2 + omega6_log2 +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian())
svyvif(mod, X = data.frame(X[,-1]), w = data.frame(df[df$use_fat_covar,])$WTDN4YR)
#                                         svy.vif.m  reg.vif.m      zeta     varrho.m zeta.x.varrho.m      Rsq.m
# omega3_log2                              3.151974   3.212232 1257285.5 7.804443e-07       0.9812413 0.68868994
# omega6_log2                              3.702299   3.694117 1360590.3 7.366028e-07       1.0022147 0.72929935

# PhenoAge
i = 7
mod = svyglm(formula(paste0(vars_ead[i], " ~ omega3_log2 + omega6_log2 +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian())
svyvif(mod, X = data.frame(X[,-1]), w = data.frame(df[df$use_fat_covar,])$WTDN4YR)
#                                         svy.vif.m  reg.vif.m      zeta     varrho.m zeta.x.varrho.m      Rsq.m
# omega3_log2                              2.961911   3.212232 2113404.1 4.362974e-07       0.9220726 0.68868994
# omega6_log2                              3.514716   3.694117 2519250.1 3.776663e-07       0.9514360 0.72929935

# GrimAge2
i = 8
mod = svyglm(formula(paste0(vars_ead[i], " ~ omega3_log2 + omega6_log2 +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian())
svyvif(mod, X = data.frame(X[,-1]), w = data.frame(df[df$use_fat_covar,])$WTDN4YR)
#                                         svy.vif.m  reg.vif.m      zeta     varrho.m zeta.x.varrho.m      Rsq.m
# omega3_log2                              3.175466   3.212232  854816.1 1.156453e-06       0.9885546 0.68868994
# omega6_log2                              3.717093   3.694117  788996.5 1.275316e-06       1.0062196 0.72929935

# DNAmTL
i = 9
mod = svyglm(formula(paste0(vars_ead[i], " ~ omega3_log2 + omega6_log2 +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian())
svyvif(mod, X = data.frame(X[,-1]), w = data.frame(df[df$use_fat_covar,])$WTDN4YR)
#                                         svy.vif.m  reg.vif.m      zeta     varrho.m zeta.x.varrho.m      Rsq.m
# omega3_log2                              2.829337   3.212232 2170.4203 0.0004058205       0.8808010 0.68868994
# omega6_log2                              3.487489   3.694117 2832.5737 0.0003332890       0.9440657 0.72929935

# YangCell
i = 10
mod = svyglm(formula(paste0(vars_ead[i], " ~ omega3_log2 + omega6_log2 +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian())
svyvif(mod, X = data.frame(X[,-1]), w = data.frame(df[df$use_fat_covar,])$WTDN4YR)
#                                         svy.vif.m  reg.vif.m      zeta     varrho.m zeta.x.varrho.m      Rsq.m
# omega3_log2                              3.449913   3.212232 34265.484 3.134328e-05       1.0739926 0.68868994
# omega6_log2                              3.497886   3.694117 33411.856 2.833964e-05       0.9468801 0.72929935

# DunedinPoAm
i = 11
mod = svyglm(formula(paste0(vars_ead[i], " ~ omega3_log2 + omega6_log2 +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian())
svyvif(mod, X = data.frame(X[,-1]), w = data.frame(df[df$use_fat_covar,])$WTDN4YR)
#                                         svy.vif.m  reg.vif.m      zeta     varrho.m zeta.x.varrho.m      Rsq.m
# omega3_log2                              2.929468   3.212232 34781.148 2.622032e-05       0.9119727 0.68868994
# omega6_log2                              3.428352   3.694117 35402.935 2.621413e-05       0.9280572 0.72929935
```


```{r, warning=FALSE, message=FALSE, echo = F}
kable(fat_res_alcSmkAct_omegas) %>% kable_classic()
```


#### Associations with individual fatty acids
```{r, eval = F}
# dataframe to store results
subtypes_res = data.frame(nutrient = rep(c('SFA 4:0', 'SFA 6:0', 'SFA 8:0', 'SFA 10:0', 'SFA 12:0', 'SFA 14:0', 'SFA 16:0', 'SFA 18:0',
                            'MUFA 16:1', 'MUFA 18:1', 'MUFA 20:1', 'MUFA 22:1',
                            'PUFA 18:2', 'PUFA 20:4', 'PUFA 18:3', 'PUFA 20:5', 'PUFA 22:5', 'PUFA 22:6'), each = 11),
  clock = rep(c('Horvath1', 'Horvath2', 'Hannum', 'Lin', 'Zhang', 'VidalBralo', 'PhenoAge', 'GrimAge2', 
        'DNAmTL', 'YangCell', 'DunedinPoAm'), times = 18),
  coef = NA, p = NA, CI_L = NA, CI_H = NA, n = NA)

# NHANES variable names
vars_ead = c("HorvathAge", "SkinBloodAge", "HannumAge", "LinAge", "ZhangAge", "VidalBraloAge", "PhenoAge", "GrimAge2Mort", "HorvathTelo", "YangCell_scale", "DunedinPoAm_scale")
subtypes = c("DRXTS040_log2", "DRXTS060_log2", "DRXTS080_log2", "DRXTS100_log2", "DRXTS120_log2", "DRXTS140_log2", "DRXTS160_log2", "DRXTS180_log2", "DRXTM161_log2", 
        "DRXTM181_log2", "DRXTM201_log2", "DRXTM221_log2", "DRXTP182_log2", "DRXTP204_log2", "DRXTP183_log2", "DRXTP205_log2", "DRXTP225_log2", "DRXTP226_log2")

# functions to fill in table
popTable1_subtypes = function(tab, i, j, k){
    # i = EAD variable
    # j = fat variable
    # k = table row
    mod = svyglm(formula(paste0(vars_ead[i], " ~ ", subtypes[j], " +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian())
    tab[k,3] = summary(mod)$coef[2,1]
    tab[k,4] = summary(mod)$coef[2,4]
    tab[k,5] = confint(mod)[2,1]
    tab[k,6] = confint(mod)[2,2]
    tab[k,7] = nrow(mod$model)
    return(tab)
}

popTable2_subtypes = function(tab, subtypes, vars_ead){
    k = 1
    for (j in 1:length(subtypes)){
        for (i in 1:length(vars_ead)){
            tab = popTable1_subtypes(tab, i, j, k)
            k = k + 1
        }
    }
    return(tab)
}

subtypes_res = popTable2_subtypes(subtypes_res, subtypes, vars_ead)
subtypes_res$B_CI = paste0(round(subtypes_res$coef, 2), ' (', round(subtypes_res$CI_L, 2), ', ', round(subtypes_res$CI_H, 2), ')')

write.csv(subtypes_res, 'subtypes_res_noScale.csv')


# results for plotting
# dataframes to store results
type_B = data.frame(matrix(nrow = 18, ncol = 11))
rownames(type_B) = subtypes
colnames(type_B) = c("HorvathAge", "SkinBloodAge", "HannumAge", "LinAge", "ZhangAge", "VidalBraloAge", "PhenoAge", "GrimAge2Mort", "HorvathTelo", "YangCell_scale", "DunedinPoAm")
type_p = type_B

for (i in 1:nrow(type_B)){
    for (j in 1:ncol(type_B)){
        coef = summary(svyglm(formula(paste0("scale(", colnames(type_B)[j], ") ~ ", rownames(type_B)[i], " +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian()))$coef
        type_B[i,j] = coef[2,1]
        type_p[i,j] = coef[2,4]
    }
}

write.csv(type_B, 'subtypes_B.csv')
write.csv(type_p, 'subtypes_p.csv')
```

```{r, warning=FALSE, message=FALSE, echo = F}
kable(subtypes_res) %>% kable_classic()
```


## Sensitivity analyses with imputed covatiates
```{r, eval = F}
load("nhanes_fattyAcids_clean_data.RData")
set.seed(123)

df_use = df[df$use_fat,]

# check that covariates are coded as numbers
table(df_use$RIAGENDR)

table(df_use$RIDRETH1)

table(df_use$active_modvig)
#   No  Yes 
# 1197 1022
df_use$active_modvig = ifelse(df_use$active_modvig == 'No', 0,
                        ifelse(df_use$active_modvig == 'Yes', 1, NA))
table(df_use$active_modvig)
#    0    1 
# 1197 1022 

table(df_use$SMOKE_3cat)
#   Never  Former Current 
#     1004     863     349  
df_use$SMOKE_3cat <- ifelse(df_use$SMOKE_3cat == "Never", 0, 
                        ifelse(df_use$SMOKE_3cat == "Former", 1, 
                        ifelse(df_use$SMOKE_3cat == "Current", 2, NA)))
table(df_use$SMOKE_3cat)
#    0    1    2 
# 1004  863  349 

table(df_use$EDUCATION)
# High School Diploma (including GED)               Less Than High School               More Than High School 
#                                455                                 995                                 770 
df_use$EDUCATION <- ifelse(df_use$EDUCATION == "Less Than High School", 0, 
                        ifelse(df_use$EDUCATION == "High School Diploma (including GED)", 1, 
                        ifelse(df_use$EDUCATION == "More Than High School", 2, NA)))
table(df_use$EDUCATION)     
#    0    1    2 
#   995 455 770  

table(df_use$OCCUPATION)
#   hiblue  hiwhite  lowblue lowwhite   nowork 
#       301      505      857      376       55 
df_use$OCCUPATION <- ifelse(df_use$OCCUPATION == "lowblue", 0, ifelse(df_use$OCCUPATION == "hiblue", 1, 
                ifelse(df_use$OCCUPATION == "lowwhite", 2, ifelse(df_use$OCCUPATION == "hiwhite", 3, 
                                                       ifelse(df_use$OCCUPATION == "nowork", 4, NA)))))
table(df_use$OCCUPATION)
#   0   1   2   3   4 
# 857 301 376 505  55  

df_use$RIAGENDR <- as.factor(df_use$RIAGENDR)
df_use$RIDRETH1 <- as.factor(df_use$RIDRETH1)
df_use$EDUCATION <- as.factor(df_use$EDUCATION)
df_use$OCCUPATION <- as.factor(df_use$OCCUPATION)
df_use$SMOKE_3cat <- as.factor(df_use$SMOKE_3cat)
df_use$INDFMPIR <- as.numeric(df_use$INDFMPIR)   
df_use$active_modvig <- as.numeric(df_use$active_modvig)

# subset dataset to just covariates
# mice will try to impute any missing value so will rejoin imputed covariates with the exposures/outcomes after
subs <- df_use %>% 
  dplyr::select(RIDAGEYR, RIAGENDR, RIDRETH1, BMXBMI, DRXTKCAL, active_modvig, EDUCATION, OCCUPATION, INDFMPIR, drinkvol, SMOKE_3cat)
non_subs <- df_use %>% 
  dplyr::select(-RIDAGEYR, -RIAGENDR, -RIDRETH1, -BMXBMI, -DRXTKCAL, -active_modvig, -EDUCATION, -OCCUPATION, -INDFMPIR, -drinkvol, -SMOKE_3cat)

df_imp <- mice(subs, m = 5)              # imputation with 5 iterations 
df_imp <- mice::cbind(df_imp, non_subs)  # rejoin exposure/outcome data

# output is 5 iterations of complete datasets, each iteration can be accessed with the complete function
table(df_use$OCCUPATION)                            # original non-imputer values
#   0   1   2   3   4 
# 857 301 376 505  55
table(complete(df_imp, action = 2)$OCCUPATION)  # after imputation from the 2nd iteration
#   0   1   2   3   4 
# 928 310 399 524  59 


# create imputation list compatible with survey design
l <- list((complete(df_imp, action = 1)), (complete(df_imp, action = 2)), (complete(df_imp, action = 3)), 
          (complete(df_imp, action = 4)), (complete(df_imp, action = 5)))
df_imp_list <- imputationList(l) 

# specify survey design
nhanesDesign_impute <- svydesign(id = ~SDMVPSU,  # Primary Sampling Units (PSU)
                          strata  = ~SDMVSTRA, # Stratification used in the survey
                          weights = ~WTDN4YR,   # Survey weights (using those from DNAm dataset)
                          nest    = TRUE,      # Whether PSUs are nested within strata
                          data    = df_imp_list)  # only change from non-imputed version

dim(nhanesDesign_impute)
# 2220  288    5
```


### Associations with fatty acid intake
```{r, eval = F}
fat_res_alcSmkAct_imp = data.frame(nutrient = rep(c('Total fat', 'Saturated fat', 'Monounsaturated fat', 'Polyunsaturated fat', 'P:S ratio', 'Omega-3', 'Omega-6'), each = 11),
  clock = rep(c('Horvath1', 'Horvath2', 'Hannum', 'Lin', 'Zhang', 'VidalBralo', 'PhenoAge', 'GrimAge2', 
        'DNAmTL', 'YangCell', 'DunedinPoAm'), times = 7),
  coef = NA, p = NA, CI_L = NA, CI_H = NA)

# NHANES variable names
# vars_fat = c('DRXTTFAT', 'DRXTSFAT', 'DRXTMFAT', 'DRXTPFAT', 'psatfatRatio', 'psatfatRatioGt1', 'omega3', 'omega6', 'omegaRatio', 'omegaRatio5')
vars_fat = c('DRXTTFAT_log2', 'DRXTSFAT_log2', 'DRXTMFAT_log2', 'DRXTPFAT_log2', 'psatfatRatio', 'omega3_log2', 'omega6_log2')
vars_ead = c('HorvathAge', 'SkinBloodAge', 'HannumAge', 'LinAge', 'ZhangAge', 'VidalBraloAge', 'PhenoAge', 'GrimAge2Mort', 'HorvathTelo', 'YangCell_scale', 'DunedinPoAm_scale')


# functions to fill in table
popTable1 = function(tab, i, j, k){
    # i = EAD variable
    # j = OCM variable
    # k = table row
    mod <- with(nhanesDesign_impute, svyglm(formula(paste0(vars_ead[i], " ~ ", vars_fat[j], " +
        RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
        BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
        factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
                        subset = use,
                        design = nhanesDesign_impute, 
                        family = gaussian()))
    tab[k,3] = summary(pool(mod), conf.int = TRUE)[2,2]
    tab[k,4] = summary(pool(mod), conf.int = TRUE)[2,6]
    tab[k,5] = summary(pool(mod), conf.int = TRUE)[2,7]
    tab[k,6] = summary(pool(mod), conf.int = TRUE)[2,8]
    return(tab)
}

popTable2 = function(tab, vars_fat, vars_ead){
    k = 1
    for (j in 1:length(vars_fat)){
        for (i in 1:length(vars_ead)){
            tab = popTable1(tab, i, j, k)
            k = k + 1
        }
    }
    return(tab)
}

fat_res_alcSmkAct_imp = popTable2(fat_res_alcSmkAct_imp, vars_fat, vars_ead)

fat_res_alcSmkAct_imp$B_CI = paste0(round(fat_res_alcSmkAct_imp$coef, 2), ' ', fat_res_alcSmkAct_imp$CI)

write.csv(fat_res_alcSmkAct_imp, 'fat_res_alcSmkAct_imp.csv')
```


```{r, warning=FALSE, message=FALSE, echo = F}
kable(fat_res_alcSmkAct_imp) %>% kable_classic()
```


#### Associations with individual fatty acids
```{r, eval = F}
# without scaling epigenetic age variables
vars_ead = c("HorvathAge", "SkinBloodAge", "HannumAge", "LinAge", "ZhangAge", "VidalBraloAge", "PhenoAge", "GrimAge2Mort", "HorvathTelo", "YangCell_scale", "DunedinPoAm_scale")
subtypes = c("DRXTS040_log2", "DRXTS060_log2", "DRXTS080_log2", "DRXTS100_log2", "DRXTS120_log2", "DRXTS140_log2", "DRXTS160_log2", "DRXTS180_log2", "DRXTM161_log2", 
        "DRXTM181_log2", "DRXTM201_log2", "DRXTM221_log2", "DRXTP182_log2", "DRXTP204_log2", "DRXTP183_log2", "DRXTP205_log2", "DRXTP225_log2", "DRXTP226_log2")

subtypes_res_imp = data.frame(nutrient = rep(c('SFA 4:0', 'SFA 6:0', 'SFA 8:0', 'SFA 10:0', 'SFA 12:0', 'SFA 14:0', 'SFA 16:0', 'SFA 18:0',
                            'MUFA 16:1', 'MUFA 18:1', 'MUFA 20:1', 'MUFA 22:1',
                            'PUFA 18:2', 'PUFA 20:4', 'PUFA 18:3', 'PUFA 20:5', 'PUFA 22:5', 'PUFA 22:6'), each = 11),
  clock = rep(c('Horvath1', 'Horvath2', 'Hannum', 'Lin', 'Zhang', 'VidalBralo', 'PhenoAge', 'GrimAge2', 
        'DNAmTL', 'YangCell', 'DunedinPoAm'), times = 18),
  coef = NA, p = NA, CI_L = NA, CI_H = NA)

# functions to fill in table
popTable1_subtypes_imp = function(tab, i, j, k){
    # i = EAD variable
    # j = fat variable
    # k = table row
    mod = with(nhanesDesign_impute, svyglm(formula(paste0(vars_ead[i], " ~ ", subtypes[j], " +
            RIDAGEYR + I(RIDAGEYR^2) + factor(RIAGENDR) + factor(RIDRETH1) +
            BMXBMI + DRXTKCAL + factor(SMOKE_3cat) + drinkvol + factor(active_modvig) +
            factor(EDUCATION) + factor(OCCUPATION) + INDFMPIR")),
            design = nhanesDesign_use, 
            family = gaussian()))
    tab[k,3] = summary(pool(mod), conf.int = TRUE)[2,2]
    tab[k,4] = summary(pool(mod), conf.int = TRUE)[2,6]
    tab[k,5] = summary(pool(mod), conf.int = TRUE)[2,7]
    tab[k,6] = summary(pool(mod), conf.int = TRUE)[2,8]
    return(tab)
}

popTable2_subtypes_imp = function(tab, subtypes, vars_ead){
    k = 1
    for (j in 1:length(subtypes)){
        for (i in 1:length(vars_ead)){
            tab = popTable1_subtypes_imp(tab, i, j, k)
            k = k + 1
        }
    }
    return(tab)
}

subtypes_res_imp = popTable2_subtypes_imp(subtypes_res_imp, subtypes, vars_ead)
subtypes_res_imp$B_CI = paste0(round(subtypes_res_imp$coef, 2), ' (', round(subtypes_res_imp$CI_L, 2), ', ', round(subtypes_res_imp$CI_H, 2), ')')
write.csv(subtypes_res_imp, 'subtypes_res_noScale_imp.csv')
```

```{r, warning=FALSE, message=FALSE, echo = F}
kable(subtypes_res_imp) %>% kable_classic()
```
